Challenges and Solutions of Developing and Implementing a Revolutionary Novel Desktop-as-a-Service

### 2024-04-23 paper.tex
More content for section 4.1 (compatibility)

The first relevant characteristic of a DaaS that a user is confronted with is the list of compatible applications. In the best case, all applications of all popular operating systems can be integrated and used with such a novel platform. Several DaaS projects and solutions from the last two decades, as well as similar concepts like web desktops or webtops, lacked native support for popular everyday applications.

Examples worth mentioning in this context is eyeOS (2005)~\cite{liu2012research}~\cite{vidyabanu2011implementation}, which simulated a desktop environment using HTML, PHP, JavaScript, and MySQL. Despite being open source, it has never become widely used since it is impossible to import and use native Windows or Linux applications with this software. All required applications have to be developed as web applications.

Kommerzielle Anwendungen...

Anwendungen (Windows / Linux / MacOS)

>>>>

The first relevant characteristic of a DaaS that a user is confronted with is the list of compatible applications. In the best case, all applications of all popular operating systems can be integrated and used with such a novel platform. Several DaaS projects and solutions from the last two decades and similar concepts like web desktops or webtops lacked native support for popular everyday applications.

Examples worth mentioning in this context is eyeOS (2005)~\cite{liu2012research}~\cite{vidyabanu2011implementation}, which simulated a desktop environment using HTML, PHP, JavaScript, and MySQL. Despite being open source, it has never become widely used since it is impossible to import and use native Windows or Linux applications with this software. All required applications have to be developed as web applications. This limitation especially caused most potential users to lose interest in web desktops because many popular native applications can hardly be replaced or re-developed, and many feature-rich and well-established Software-as-a-Service offerings like Microsoft Office 365 and Google Docs already exist.

The development of DaaS solutions in the past shows that a new DaaS will only be accepted by a broad user group if it enables the integration of native applications in an unchanged manner. It is also desirable that a DaaS supports applications for the Linux and Windows operating systems to enable flexible working and make the operation of a virtualization solution on the desktops unnecessary. Ideally, it should also be possible to run native MacOS applications. However, this goal is difficult to achieve under legal conditions due to the licensing restrictions of the MacOS operating system.
